### 2012-05-23 inst/examples/policycosts/exact_npv.Rmd
npv_exact figure2

```{r comparison}
closest <- function(x, v){
	which.min(abs(v-x))
}

ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
cbind(index, c2=c2[index$V1])
````

>>>>

```{r comparison_plot}
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

```{r numeric_value}
closest <- function(x, v){
	which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
cbind(index, c2=c2[index$V1])
````
